### 2014-10-22 old_notes/model_10_03_12.tex
ive added code for tracking mutual information over time and changed figures a bit

\documentclass{article}
\usepackage{custom2}
\usepackage{graphicx} % for figures
\usepackage{caption}
\usepackage{subcaption}
\usepackage{epstopdf} % so can use EPS or PDF figures
\usepackage{subfig}
\usepackage{url}
\usepackage{amssymb,amsfonts}
\usepackage[all,arc]{xy}
\usepackage{enumerate}
\usepackage{mathrsfs}
\captionsetup{justification=RaggedRight, singlelinecheck=false}

@@

\begin{center}
{\bf \LARGE{Development of a Signaling Network}}
\vspace{10pt}
\\ Eleanor Brush
\\ August 29, 2012
\end{center}

@@

\begin{align*}
\frac{dx}{dt}&=m_ex+m_f+bf(y)
\\ \frac{dy}{dt}&=m_ey-m_f+bf(x)
\end{align*}
If $b=0$, there is an equilibrium at $(x,y)=\left(-\frac{m_f}{m_e},\frac{m_f}{m_e}\right).$  If $b\neq 0$, we can find equilibrium by solving $\frac{dx}{dt}=\frac{dy}{dt}=0$.  We assume that $f(x)=1$ for $x<-T$ and $f(x)=0$ for $x>-T$.
\begin{enumerate}
\item $\left(\frac{-m_f}{m_e},\frac{m_f}{m_e}\right)$ if $\frac{-m_f}{m_e}>-T$ and $\frac{m_f}{m_e}>-T$
\item $\left(\frac{-m_f}{m_e},\frac{m_f-b}{m_e}\right)$ if $\frac{-m_f}{m_e}<-T$ and $\frac{m_f-b}{m_e}>-T$
\item $\left(\frac{-m_f-b}{m_e},\frac{m_f}{m_e}\right)$ if $\frac{-m_f-b}{m_e}>-T$ and $\frac{m_f}{m_e}<-T$
\item $\left(\frac{-m_f-b}{m_e},\frac{m_f-b}{m_e}\right)$ if $\frac{-m_f-b}{m_e}<-T$ and $\frac{m_f-b}{m_e}<-T$
\end{enumerate}
Errors only provide negative feedback and prevent escalation when $m_e\leq 0$.  In this case, equilibria $2.$ and $4.$ are impossible since $-m_f,-m_f-b<0$ $\Rightarrow$ $\frac{-m_f}{m_e},\frac{-m_f-b}{m_e}>0$ while $-T<0$.  Therefore, no equilibria where Animal 1 is signaling is possible.  So we are left with 
\begin{enumerate}
\item $\left(\frac{-m_f}{m_e},\frac{m_f}{m_e}\right)$ if $\frac{m_f}{m_e}>-T$
\item $\left(\frac{-m_f-b}{m_e},\frac{m_f}{m_e}\right)$ if $\frac{m_f}{m_e}<-T$
\end{enumerate}
Note that if $b=0$, the equilibria are identical.  Equilibrium $1.$ is only possible if $\frac{m_f}{m_e}>-T$ while $2.$ is only possible if $\frac{m_f}{m_e}<-T$ so that the relative strength of the effects from fights and errors determines which equilibria is possible.  If $m_f$ is small, an equilibrium with neither animal signaling is possible, whereas is $m_f$ is sufficiently large at equilibrium Animal 2 will signal Animal 1 and Animal 1's estimate is boosted by $\frac{b}{-m_e}$.  In either case, Animal 2's equilibrium estimate is the same.

The Jacobian of this system at an equilibrium is
$$
J=\left[
\begin{array}{ccccc}
m_e & bf'(y^*) \\
bf'(x^*) & m_e
\end{array}\right] $$
with eigenvalues
$$\lambda=m_e\pm  \frac{b}{2}\sqrt{f'(y^*)f'(x^*)}.$$

Since we have assumed that $f$ is non-increasing everywhere, $f'(x)<0$ everywhere and both eigenvalues are real.  If $m_e<0$, the eigenvalue with greater absolute value will be 
$$\lambda=m_e- \frac{b}{2} \sqrt{f'\left(\frac{m_f}{m_e}\right)f'\left(x^*\right)}$$
since for both possible equilibria $y^*=\frac{m_f}{m_e}$.  In addition, $\lambda<0$ so that both equilibria are stable.

Let $\lambda_s=m_e- \frac{b}{2}\sqrt{f'\left(\frac{m_f}{m_e}\right)f'\left(\frac{-m_f}{m_e}\right)}$ and $\lambda_{ns}=m_e-  \frac{b}{2}\sqrt{f'\left(\frac{m_f}{m_e}\right)f'\left(\frac{-m_f-b}{m_e}\right)}$ so that $\lambda_s$ is the eigenvalue associated with the equilibrium where Animal 2 signals and $\lambda_{ns}$ is the eigenvalue associated with the equilibrium where Animal 2 is not signaling.  There are two effects of signaling feedbacks on these eigenvalues.  First, when $b\gneq 0$, both $\lambda_s$ and $\lambda_{ns}$ decrease so that the decay to the equilibria is faster when the estimates are influenced by signaling behaviors.

If we further assume that $f$ is a decreasing sigmoid, then $f'$ is decreasing for $x<-T$ and increasing for $x>-T$ so that $0<\left|f'\left(\frac{-m_f-b}{m_e}\right)\right|<\left|f'\left(\frac{-m_f}{m_e}\right)\right|$.  Therefore, $0>\lambda_s>\lambda_{ns}$.  In general, this suggests that (SMALL!) perturbations around the non-signaling equilibrium, $\left(\frac{-m_f}{m_e},\frac{m_f}{m_e}\right)$, will shrink faster than (SMALL!) perturbations around the signaling equilibrium, $\left(\frac{-m_f-b}{m_e},\frac{m_f}{m_e}\right)$.  This effect is greater when the transition from non-signaling to signaling behavior as a function of $x$ is shallower: when the transition is steep, $f'(x)$ is essentially zero for $x>-T$ so that there is only a negligible difference between $f'\left(\frac{-m_f}{m_e},\frac{m_f}{m_e}\right)$ and $f'\left(\frac{-m_f-b}{m_e},\frac{m_f}{m_e}\right)$

>>>>

\documentclass{article}
\usepackage{latexsym}
\usepackage{amssymb,amsmath}
\usepackage{custom2}
\usepackage{graphicx} % for figures
\usepackage{epstopdf} % so can use EPS or PDF figures
\usepackage{caption}
\usepackage{subcaption}
\usepackage{url}
\usepackage{amssymb,amsfonts}
\usepackage[all,arc]{xy}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage{booktabs}
\usepackage[pdftex]{hyperref}
\usepackage{lscape}
\captionsetup{justification=RaggedRight, singlelinecheck=false}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
\newcommand{\argmax}{\text{argmax}}
\newcommand{\Tr}{\text{Tr}}
%\newtheorem{claim}{Claim}

@@

\begin{center}
{\bf \LARGE{Development of a Signaling Network}}
\vspace{10pt}
\\ Eleanor Brush
\\ October 03, 2012
\end{center}

\tableofcontents

@@

\begin{align*}
\frac{dx}{dt}&=-ex+f+br(y+T)
\\ \frac{dy}{dt}&=-ey-f+br(x+T)
\end{align*}

The isoclines of this system are given by
\begin{align*}
\dot{x}=0 \Rightarrow x&=\frac{f}{e}+\frac{b}{e}r(y+T) 
\\\dot{y}=0 \Rightarrow y&=-\frac{f}{e}+\frac{b}{e}r(x+T)
\end{align*}

The Jacobian of this system is given by
$$J(x,y)=\left(\begin{array}{cccc} 
-e & br'(y+T)
\\ br'(x+T) & -e
\end{array}\right)$$
Letting $\tau=Tr(J(x,y))$ and $\Delta=\text{det}(J(x,y)),$ we see that $\tau=-2e$ and $\Delta=e^2-b^2r'(y+T)r'(x+T)$.  Since $e>0$, $\tau<0$ and any fixed point will be a saddle point, a stable sink, or a stable spiral, depending on the sign of $\Delta$.  
\begin{align*}
\Delta<0 &\Leftrightarrow e^2-b^2r'(y+T)r'(x+T)<0 
\\&\Leftrightarrow e<b\sqrt{r'(y+T)r'(x+T)} \text{ since } e,b, \text{ and } r'(y+T)r'(x+T)\geq0
\\ &\Leftrightarrow \left\{\begin{array}{cccc}
b>0 & \text{ if } e=0
\\ b>2\epsilon e & \text{ if } e>0
\end{array}\right.
\end{align*}
Therefore, if there is a fixed point with $r'(y+T)\neq 0$ and $r'(x+T)\neq 0$ (i.e. the isoclines cross where their slopes are not zero), the fixed point is a saddle and there are two other stable fixed points only if $b>2\epsilon e$.  Other conditions are required, as well.  In the following, we let $c=\frac{f}{e}$.  Then we also need
\begin{align}
-T+\epsilon&<-c+\frac{b}{e}r(c+T) \label{cond1} 
\\ -T-\epsilon&>-c+\frac{b}{e}r(c+\frac{b}{e}+T) \label{cond2}
\end{align}

These lead to the following conditions on $\frac{f}{e}=c$:
\begin{align}
(\ref{cond1}) \Rightarrow -T+\epsilon&<-c-\frac{b}{2\epsilon e}c-\frac{bT}{2\epsilon e}+\frac{b}{2e} \notag
\\ \Rightarrow c&<\left(\frac{2\epsilon e-b}{2\epsilon e+b}\right)T-\frac{2\epsilon^2e}{2\epsilon e+b}+\frac{\epsilon b}{2\epsilon e+b}=:M \label{xmax}
\\ (\ref{cond2}) \Rightarrow -T-\epsilon&>-c-\frac{b}{2\epsilon e}c-\frac{b^2}{2\epsilon e^2}-\frac{bT}{2\epsilon e}+\frac{b}{2e} \notag
\\ \Rightarrow c&>\left(\frac{2\epsilon e-b}{2\epsilon e+b}\right)T+\frac{2\epsilon^2e-b^2/e}{2\epsilon e +b}+\frac{\epsilon b}{2\epsilon e+b}=:m \label{xmin}
\end{align}
Note that $m<M$ if and only if $b>2\epsilon e$, so that $m$ and $M$ are valid lower and upper bounds on $x$ only if $b$ is sufficiently large for a saddle point to exist.  Equations (\ref{xmax}) and (\ref{xmin}) can be rewritten to provide bounds on $T$ that allow a bifurcation to occur:
\begin{align}
(\ref{xmax}) \Rightarrow(2\epsilon e-b)T&>  (2\epsilon e+b)c +2\epsilon^2e-\epsilon b \notag
\\ \Rightarrow  T&<\frac{(2\epsilon e+b)c+2\epsilon^2e-\epsilon b}{2\epsilon e-b}  \notag
\\ \Rightarrow T&< \frac{ 2\epsilon e(c+\epsilon)+b(c-\epsilon)}{2\epsilon e-b}\label{tmax}
\\(\ref{xmin}) \Rightarrow (2\epsilon e-b)T&< (2\epsilon e+b)c-2\epsilon^2e+b^2/e-\epsilon b \notag
\\ \Rightarrow  T&>\frac{(2\epsilon e+b)c-2\epsilon^2e+b^2/e-\epsilon b}{2\epsilon e-b}\notag
\\ \Rightarrow T&> \frac{2\epsilon e(c-\epsilon)+b(c-\epsilon+b/e)}{2\epsilon e-b} \label{tmin}
\end{align}
If the equivalent conditions (\ref{cond1}),(\ref{xmax}),(\ref{tmax}) are violated, there can be no stable fixed point with animal 1 signaling at a nonzero rate and animal 2 not signaling because the difference in fighting ability is too great or the threshold below which signaling occurs is too low.

Another interesting phenomenon is the possibility of each animal signaling the other at a non-zero rate.  In order for this to occur, we need $\dot{x}(x,-\frac{f}{e})<0$ for al $x>x^*$ and in particular for $x=-T+\epsilon$ so that
\begin{align*}
-e(-T+\epsilon)+f+br(-\frac{f}{e}+T)&<0
\\ \Rightarrow-T+\epsilon&>c+\frac{b}{e}r(-\frac{f}{e}+T)
\\ \Rightarrow -T+\epsilon&>c+\frac{b}{e}\left(\frac{c}{2\epsilon}-\frac{T}{2\epsilon}+\frac{1}{2}\right)
\\ \Rightarrow \frac{(b-2\epsilon e)}{2\epsilon e}T&>c-\epsilon+\frac{bc}{2\epsilon e}+\frac{b}{2e}
\\ \Rightarrow (b-2\epsilon e)T&>2\epsilon e(c-\epsilon)+bc+b\epsilon
\\ \Rightarrow T&<\frac{2\epsilon e(\epsilon -c)-b(c+\epsilon)}{2\epsilon e-b} 
\end{align*}
where the last inequality follows because this can only happen if $b<2\epsilon e$.  (The condition $b<2\epsilon e$ is equivalent to the slope of the $x$ isocline being steeper than the slop of the $y$ isocline where they have non-zero slopes.  Otherwise, if $x$ and $y$ are both signaling at non-zero rates, a bifurcation will occur.)

Note that if $f>0$ so that $\frac{f}{e}>-T-\epsilon,$ there can be no steady state with animal $1$ signaling at rate $=1$.  The possible steady states are as follows:
\begin{enumerate}
\item Neither animal signaling:
\begin{align*}
\Rightarrow -T+\epsilon< \frac{f}{e} \text{ and } -T+\epsilon<-\frac{f}{e}
\\ \Rightarrow T>\epsilon-\frac{f}{e} \text{ and } T> \epsilon+\frac{f}{e}
\\ \Rightarrow T>\epsilon+\frac{f}{e}
\end{align*}
\item Animal 1 not signaling, animal 2 signaling at a rate $\in(0,1)$:
\begin{enumerate}
\item 
\begin{align*}
-T-\epsilon<-\frac{f}{e}
\\ \Rightarrow T>\frac{f}{e}-\epsilon
\end{align*}
\item \begin{align*}
\frac{f}{e}+\frac{b}{e}r\left(-\frac{f}{e}+T\right)>-T+\epsilon&>\max\left\{-\frac{f}{e}+\frac{b}{e}r\left(\frac{f}{e}+T\right),-\frac{f}{e}\right\}
\\ \Rightarrow \epsilon-\frac{f}{e}-\frac{b}{e}r\left(-\frac{f}{e}+T\right)<T&<\epsilon-\max\left\{-\frac{f}{e}+\frac{b}{e}r\left(\frac{f}{e}+T\right),-\frac{f}{e}\right\}
\\ \Rightarrow \epsilon-\frac{f}{e}-\frac{b}{e}r\left(-\frac{f}{e}+T\right)<T&<\min\left\{\epsilon+\frac{f}{e}-\frac{b}{e}r\left(\frac{f}{e}+T\right),\epsilon+\frac{f}{e}\right\}
\\ \Rightarrow \left\{\begin{array}{cccc} 
\frac{2\epsilon e(\epsilon -\frac{f}{e})+b(-\frac{f}{e}-\epsilon)}{2\epsilon e-b}<T<\epsilon+\frac{f}{e} &\text{ if } b<2\epsilon e
\\\frac{2\epsilon e(\epsilon +\frac{f}{e})+b(\frac{f}{e}-\epsilon)}{2\epsilon e-b}<T<\epsilon+\frac{f}{e} &\text{ if } b>2\epsilon e
\end{array}\right.
\end{align*}
\end{enumerate}
\item Animal 1 not signaling, animal 2 signaling at rate $=1$:
\begin{enumerate}
\item 
\begin{align*}
-T-\epsilon&>-\frac{f}{e}
\\ \Rightarrow T&<\frac{f}{e}-\epsilon
\end{align*}
Therefore, for the following condition we assume that $\frac{f}{e}-\epsilon>0$ so that $\epsilon-\frac{f}{e}<0$.
\item 
\begin{align*}
\frac{f}{e}+\frac{b}{e}>-T+\epsilon&>-\frac{f}{e}+\frac{b}{e}r\left(\frac{f}{e}+T\right)
\\ \Rightarrow \epsilon-\frac{f}{e}-\frac{b}{e}<T&<\epsilon+\frac{f}{e}-\frac{b}{e}r\left(\frac{f}{e}+T\right)
\\ \Rightarrow T&\left\{\begin{array}{cccc}
<\frac{2\epsilon e(\epsilon +\frac{f}{e})+b(\frac{f}{e}-\epsilon)}{2\epsilon e-b} & \text{ if } b<2\epsilon e
\\ >\frac{2\epsilon e(\epsilon +\frac{f}{e})+b(\frac{f}{e}-\epsilon)}{2\epsilon e-b} & \text{ if } b>2\epsilon e
\end{array}\right.
\\ \Rightarrow
0<T&<\frac{f}{e}-\epsilon
\end{align*}
\end{enumerate}
\item Both animals signaling at a non-zero rate, but only one steady state:
\begin{enumerate}
\item $b<2\epsilon e$ ensures that there is no unstable equilibrium, i.e. there is only one equilibrium
\item 
\begin{align*}
-T+\epsilon&>-\frac{f}{e}+\frac{b}{e}r(-\frac{f}{e}+T)
\\ \Rightarrow T&<\frac{2\epsilon e(\epsilon -\frac{f}{e})-b(\frac{f}{e}+\epsilon)}{2\epsilon e-b} 
\end{align*}

\item Two stable equilibria, one with animal 1 signaling at a non-zero rate and animal 2 not signaling and one with animal 1 not signaling and animal 2 signaling at a non-zero rate:
\begin{enumerate}
\item $b>2\epsilon e$
\item 
\begin{align*}
-T+\epsilon&<-\frac{f}{e}+\frac{b}{e}r\left(\frac{f}{e}+T\right)
\\ \Rightarrow T&>\epsilon+\frac{f}{e}-\frac{b}{e}r\left(\frac{f}{e}+T\right)
\\ \Rightarrow T&<\frac{ 2\epsilon e(\epsilon+\frac{f}{e})+b(\frac{f}{e}-\epsilon)}{2\epsilon e-b}\end{align*}
\item 
\begin{align*}
-T-\epsilon&>-\frac{f}{e}+\frac{b}{e}r\left(\frac{f}{e}+\frac{b}{e}+T\right)
\\ \Rightarrow T&>\frac{2\epsilon e(\frac{f}{e}-\epsilon)+b(\frac{f}{e}+\frac{b}{e}-\epsilon)}{2\epsilon e-b}
\\ \Rightarrow T&>0 \text{ if } b>2\epsilon e \text{ and } \frac{f}{e}<\epsilon 
\end{align*}
\end{enumerate}
(Two stable equilibria, one with animal 1 signaling at a non zero rate and animal 2 not signaling and the other with animal 1 not signaling and animal 2 signaling at rate $=1$ would require $T>\epsilon-\frac{f}{e}$ and $T<\epsilon-\frac{f}{e}$, which is clearly not possible.)
\item A single steady state with animal 1 signaling at a non-zero rate is not possible.
\end{enumerate}

Let $$\psi(b)=\frac{2\epsilon e(\epsilon -\frac{f}{e})-b(\frac{f}{e}+\epsilon)}{2\epsilon e-b} \text{ and } \varphi(b)=\frac{ 2\epsilon e(\epsilon+\frac{f}{e})+b(\frac{f}{e}-\epsilon)}{2\epsilon e-b}$$
Then, there are three general cases, depending on the magnitude of $\frac{f}{e}$ (Figure \ref{bifurcation}):
\begin{enumerate}
\item $\frac{f}{e}<\epsilon$:
\begin{enumerate}
\item neither animal signaling if $T>\epsilon+\frac{f}{e}$
\item animal 1 not signaling and animal 2 signaling at a non-zero rate if $T<\epsilon+\frac{f}{e}$ and 
$$T>\left\{\begin{array}{cccc}
\varphi(b) & \text{ if } b>2\epsilon e
\\ \psi(b) & \text{ if } b<2\epsilon e
\end{array}\right.$$

\item both animals signal at a non-zero rate if $b<2\epsilon e$ and $T<\psi(b)$
\item two stable equilibria if $b>2\epsilon e$ and $T<\varphi(b)$
\end{enumerate}
\item $\frac{f}{e}>\epsilon$:
\begin{enumerate}
\item neither animal signaling if $T>\epsilon+\frac{f}{e}$
\item animal 1 not signaling and animal 2 signaling at a non-zero rate if $T<\epsilon+\frac{f}{e}$ and $T>\frac{f}{e}-\epsilon$
\item animal 1 not signaling and animal 2 signaling at a rate $=1$ if $T<\frac{f}{e}-\epsilon$
\end{enumerate}
\end{enumerate}
In summary, when the difference in fighting ability is low, there is more uncertainty about which animal is dominant and there can even be two stable equilibria.  Once the difference in fighting ability is great enough, there can never be a stable equilibrium where the stronger animal thinks he is subordinate, but the equilibrium estimate of the weaker animal depends on the threshold below which signaling occurs.

\begin{figure}
\begin{center}
\includegraphics[width=1\textwidth]{bifurc_diagram.pdf}
\end{center}
\caption{{\bf The equilibria of the signaling model as a function of feedback level, $b$, and signaling threshold, $T$.} For both plots, $e=.5$, $\epsilon=.1$. As $f$ increases from less than $\epsilon e$ to greater than $\epsilon e$, the possible equilibria change.  \label{bifurcation}}
\end{figure}

%\frac{(2\epsilon e)(\epsilon-\frac{f}{e})-b(\frac{f}{e}+\epsilon)}{2\epsilon e-b}
%\begin{table}
%\caption{Possible equilibrium of the signaling model without stochastic dynamics.}
%\begin{tabular}{@{}lllll@{}}
%\toprule
%State & Condition on $b$ & Condition on $T$
%\\\midrule animal $1$ not signaling, animal $2$ signaling at a non-zero rate & & $T>\frac{f}{e}-\epsilon$
%\end{tabular}
%\end{table}

### 2014-10-22 old_notes/notes_signaling_model_10_03_12.tex
ive added code for tracking mutual information over time and changed figures a bit

\item Two stable equilibria, one with animal 1 signaling at a non-zero rate and animal 2 not signaling and one with animal 1 not signaling and animal 2 signaling at a non-zero rate:
\begin{enumerate}
\item $b>2\epsilon e$
\item 
\begin{align*}
-T+\epsilon&<-\frac{f}{e}+\frac{b}{e}r\left(\frac{f}{e}+T\right)
\\ \Rightarrow T&>\epsilon+\frac{f}{e}-\frac{b}{e}r\left(\frac{f}{e}+T\right)
\\ \Rightarrow T&<\frac{ 2\epsilon e(\epsilon+\frac{f}{e})+b(\frac{f}{e}-\epsilon)}{2\epsilon e-b}\end{align*}
\item 
\begin{align*}
-T-\epsilon&>-\frac{f}{e}+\frac{b}{e}r\left(\frac{f}{e}+\frac{b}{e}+T\right)
\\ \Rightarrow T&>\frac{2\epsilon e(\frac{f}{e}-\epsilon)+b(\frac{f}{e}+\frac{b}{e}-\epsilon)}{2\epsilon e-b}
\\ \Rightarrow T&>0 \text{ if } b>2\epsilon e \text{ and } \frac{f}{e}<\epsilon 
\end{align*}
\end{enumerate}
(Two stable equilibria, one with animal 1 signaling at a non zero rate and animal 2 not signaling and the other with animal 1 not signaling and animal 2 signaling at rate $=1$ would require $T>\epsilon-\frac{f}{e}$ and $T<\epsilon-\frac{f}{e}$, which is clearly not possible.)
\item A single steady state with animal 1 signaling at a non-zero rate is not possible.
\end{enumerate}

>>>>

\item Two stable equilibria, one with animal 1 signaling at a non-zero rate and animal 2 not signaling and one with animal 1 not signaling and animal 2 signaling at a non-zero rate:
\begin{enumerate}
\item $b>2\epsilon e$
\item 
\begin{align*}
-T+\epsilon&<-\frac{f}{e}+\frac{b}{e}r\left(\frac{f}{e}+T\right)
\\ \Rightarrow T&>\epsilon+\frac{f}{e}-\frac{b}{e}r\left(\frac{f}{e}+T\right)
\\ \Rightarrow T&<\frac{ 2\epsilon e(\epsilon+\frac{f}{e})+b(\frac{f}{e}-\epsilon)}{2\epsilon e-b}\end{align*}
\item 
\begin{align*}
-T-\epsilon&>-\frac{f}{e}+\frac{b}{e}r\left(\frac{f}{e}+\frac{b}{e}+T\right)
\\ \Rightarrow T&>\frac{2\epsilon e(\frac{f}{e}-\epsilon)+b(\frac{f}{e}+\frac{b}{e}-\epsilon)}{2\epsilon e-b}
\\ \Rightarrow T&>0 \text{ if } b>2\epsilon e \text{ and } \frac{f}{e}<\epsilon 
\end{align*}
\end{enumerate}
(Two stable equilibria, one with animal 1 signaling at a non zero rate and animal 2 not signaling and the other with animal 1 not signaling and animal 2 signaling at rate $=1$ would require $T<\frac{f}{e}-\epsilon$, which is negative if there is a bifurcation, so that this is not possible.

Two stable equilibria, one with animal 1 signaling at a non zero rate and animal 2 not signaling and the other with animal 1 signaling at a non-zero rate and animal 2 signaling at rate $=1$ would require $T<\epsilon-\frac{f}{e}-\frac{b}{e}\Rightarrow T<-\epsilon-\frac{f}{e}$, which is negative if there is a bifurcation, so that this is not possible.)
\item A single steady state with animal 1 signaling at a non-zero rate is not possible.
\end{enumerate}
